The impact of gas bulk rotation on the Lyman $\alpha$ line

### 2014-09-10 paper/ms.tex

%
\begin{figure*}[h]
\centerline{
\includegraphics[width=0.30\textwidth]{fig12a.pdf}
\includegraphics[width=0.30\textwidth]{fig12b.pdf}
\includegraphics[width=0.30\textwidth]{fig12c.pdf}}
\caption[]{Distribution of the cosine of the angle between the
  propagation direction and the sphere's surface. The distributions
  have been normalized to unity. Left panel: different rotational
  velocities; middle panel: different viewing angles; right panel:
  different optical depths. Only the optical depth has an effect on
  the outogoing directions. This is consistent with the assumption
  that \lya scattering in a medium with solid body rotation proceeds as in
  a static medium.}
\label{fig:surface}
\end{figure*} 
%

>>>>

%
\begin{figure*}[h]
\centerline{
\includegraphics[width=0.30\textwidth]{fig12a.pdf}
\includegraphics[width=0.30\textwidth]{fig12b.pdf}
\includegraphics[width=0.30\textwidth]{fig12c.pdf}}
\caption[]{Distribution of the cosine of the angle between the
  propagation direction and a vector normal to the sphere's
  surface. The distributions have been normalized to unity. Left
  panel: different rotational velocities; middle panel: different
  viewing angles; right panel: different optical depths. Only the
  optical depth has an effect on the distribution of outogoing
  directions. This is consistent with the assumption that \lya
  scattering in a medium with solid body rotation proceeds as in a
  static medium.} 
\label{fig:surface}
\end{figure*} 
%
